Rectangulotopes

### 2024-04-04 draft/rectangulotopes.tex
labels

@@

\section{Introduction}

\subsection{Polytopes of permutations, triangulations, and rectangulations}

@@

\subsection{Weak and strong rectangulations}

@@

@@

\subsection{Weak rectangulotopes}

@@

\subsection{Strong rectangulotopes}

@@

\subsection{Plan of the paper}

\cref{sec:quotientopes} is dedicated to the background on quotientopes and their realizations as Minkowski sums of \defn{shard polytopes}, due to A.~Padrol, V.~Pilaud, and J.~Ritter~\cite{MR4584712}, which will be our main tool throughout. \cref{sec:wr} details the case of weak rectangulations, while \cref{sec:sr} deals with strong rectangulations. In both cases, in addition to the vertex coordinates, we also give the submodular functions defining the polytopes.

@@

\subsection{Weak order and noncrossing arc diagrams}

@@

\subsection{Quotients and arc ideals}

@@

\subsection{Quotient fans and shards}

@@

\subsection{Quotientopes and shard polytopes}

@@

\section{Weak rectangulotopes}
\label{sec:wr}

%%%%%%%%%%%%

\subsection{The weak rectangulation congruence}

@@

\subsection{Up and down arcs}

@@

\subsection{Shard polytopes of up and down arcs}

@@

\subsection{Submodular functions of weak rectangulotopes}

@@

\subsection{Loday-type coordinates for weak rectangulotopes}

@@

\section{Strong rectangulotopes}
\label{sec:sr}

%%%%%%%%%%%%
\subsection{The strong rectangulation congruence}

@@

\subsection{Yin and yang arcs}

@@

\subsection{Shard polytopes of yin and yang arcs}

@@

\subsection{Submodular functions of strong rectangulotopes}

@@

\subsection{Loday-type coordinates for strong rectangulotopes}

For every rectangulation $R$, we wish to give the coordinates of a point $p(R)\in\R^n$ such that $\SRP(n)$ is the convex hull of the points $p(R)$ for all rectangulations $R$.
We first consider the contributions, to these coordinates, of the Minkowski summand $\SP(A)$ for all yin arcs $A$.
Recall that in a Minkowski sum of polytopes, the vertex that is extremal in a generic direction is the sum of the vertices of the summands that are extremal in this direction.
We therefore need to understand which vertices of the translates of the yin shard polytopes defined in \cref{lem:yinsp} are extremal for a direction given by a permutation.

@@

%%%
\newpage
\appendix
\section{Material}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

%%%%%%%%%%%%%

\subsection{Polytopes of permutations, triangulations, and rectangulations}
\label{subsec:permTrianRect}

@@

%%%%%%%%%%%%%

\subsection{Weak and strong rectangulations}
\label{subsec:weakStrongRectangulations}

@@

%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%

\subsection{Weak rectangulotopes}
\label{subsec:weakRectangulotopes}

@@

%%%%%%%%%%%%%

\subsection{Strong rectangulotopes}
\label{subsec:strongRectangulotopes}

@@

%%%%%%%%%%%%%

\subsection{Plan of the paper}
\label{subsec:plan}

\cref{sec:quotientopes} is dedicated to the background on quotientopes and their realizations as Minkowski sums of \defn{shard polytopes}, due to A.~Padrol, V.~Pilaud, and J.~Ritter~\cite{MR4584712}, which will be our main tool throughout. \cref{sec:weakRectangulotopes} details the case of weak rectangulations, while \cref{sec:strongRectangulotopes} deals with strong rectangulations. In both cases, in addition to the vertex coordinates, we also give the submodular functions defining the polytopes.

@@

%%%%%%%%%%%%%

\subsection{Weak order and noncrossing arc diagrams}
\label{subsec:noncrossingArcDiagrams}

@@

%%%%%%%%%%%%%

\subsection{Quotients and arc ideals}
\label{subsec:arcIdeals}

@@

%%%%%%%%%%%%%

\subsection{Quotient fans and shards}
\label{subsec:quotientFans}

@@

%%%%%%%%%%%%%

\subsection{Quotientopes and shard polytopes}
\label{subsec:quotientopes}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Weak rectangulotopes}
\label{sec:weakRectangulotopes}

%%%%%%%%%%%%%

\subsection{The weak rectangulation congruence}
\label{subsec:weakRectangulationCongruence}

@@

%%%%%%%%%%%%%

\subsection{Up and down arcs}
\label{subsec:upDownArcs}

@@

%%%%%%%%%%%%%

\subsection{Shard polytopes of up and down arcs}
\label{subsec:upDownShardPolytopes}

@@

%%%%%%%%%%%%%

\subsection{Submodular functions of weak rectangulotopes}
\label{subsec:submodularWeakRectangulotopes}

@@

%%%%%%%%%%%%%

\subsection{Loday coordinates of weak rectangulotopes}
\label{subsec:LodayWeakRectangulotopes}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Strong rectangulotopes}
\label{sec:strongRectangulotopes}

%%%%%%%%%%%%%

\subsection{The strong rectangulation congruence}
\label{subsec:strongRectangulationCongruence}

@@

%%%%%%%%%%%%%

\subsection{Yin and yang arcs}
\label{subsec:yinYangArcs}

@@

%%%%%%%%%%%%%

\subsection{Shard polytopes of yin and yang arcs}
\label{subsec:yinYangShardPolytopes}

@@

%%%%%%%%%%%%%

\subsection{Submodular functions of strong rectangulotopes}
\label{subsec:submodularStrongRectangulotopes}

@@

%%%%%%%%%%%%%

\subsection{Loday coordinates of strong rectangulotopes}
\label{subsec:LodayStrongRectangulotopes}

For every strong rectangulation $R$, we wish to give the coordinates of a point $\b{p}(R)\in\R^n$ such that $\SRP(n)$ is the convex hull of the points $\b{p}(R)$ for all strong rectangulations $R$.
We first consider the contributions, to these coordinates, of the Minkowski summand $\SP(A)$ for all yin arcs $A$.
%Recall that in a Minkowski sum of polytopes, the vertex that is extremal in a generic direction is the sum of the vertices of the summands that are extremal in this direction.
We need to understand which vertices of the translates of the yin shard polytopes defined in \cref{lem:yinsp} are extremal for a direction given by a permutation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\appendix
\section{Material}
